---
title: "ESF Projects"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(include = F, rows.print = 5)
library(ggplot2)
library(tidyverse)
library(readxl)
library(janitor)
bridge <- readRDS("output/geo/plz_wkr_bridge.rds")
```

The European Social Fund Plus (ESF+) is the European Union (EU)’s main instrument for investing in people and supporting the implementation of the European Pillar of Social Rights. With a budget of €142.7 billion for the period 2021-2027, the ESF+ will continue to provide an important contribution to the EU’s employment, social, education and skills policies, including structural reforms in these areas [[European Commission](https://european-social-fund-plus.ec.europa.eu/en/what-esf)].


## North Rhine Westphalia

```{r nrw, warning=FALSE}


nrw <- read_xlsx("raw/federal_states/NRW.xlsx", skip = 1, col_types = nrw_col_types) %>%
  clean_names() %>%
  filter(
    country == "DE"
  ) %>%
  select(-country) %>%
  rename(
    operation = operation_name,
    purpose = purpose_and_expected_achievements,
    cost = total_cost,
    objective = specific_objective,
    eu_cofinancing = union_co_financing_rate,
    plz = location_indicator_postal_code,
    city = location_indicator_location,
    intervention_type = interven_tion_type
  ) %>%
  mutate(
    plz = str_replace_all(plz, " ", ""),
    funding_state = "Nordrhein-Westfalen"
  )

nrw <- nrw[-c(1, 2), ]

nrw_wk <- nrw %>%
  left_join(bridge, join_by(plz))

nrw_wk_display <- nrw_wk %>%
  group_by(land_name, wkr_nr, wkr_name) %>%
  summarize(funds = sum(cost))

```
